Evolution of \\ ice sheet geometry \\ using Stokes dynamics

### 2021-06-01 talk/talk.tex
A bit more on slides.

\title{Evolution of Ice Sheet Geometry using Stokes Dynamics}

@@

\titlegraphic{\includegraphics[width=0.55\textwidth]{figs/extruded.png} \\ \includegraphics[width=0.18\textwidth]{figs/uafbw.png}}

\institute{University of Alaska Fairbanks}

\date{\phantom{foo} \bigskip \bigskip \\ SIAM GS21 \\ with assistance from Lawrence Mitchell}

@@

\vspace{-1mm}
\begin{itemize}
\item a non-shallow glacier interacting with the climate
    \begin{itemize}
    \item the simplest such problem (nonsliding, isothermal)
    \item re~\emph{steady}: solve it and you can handle implicit steps too
    \end{itemize}
\item data given on fixed $\Omega \subset \RR^2$:
    \begin{itemize}
    \item climatic mass balance $a(x,y)$ \hfill $\gets$ \emph{steady climate}
    \item bed elevation $b(x,y)$
    \end{itemize}
\item \emph{determine surface elevation $s(x,y)$ on $\Omega$ and domain $\Lambda_s \subset \RR^3$}
\end{itemize}
\end{frame}

@@

\begin{frame}{what do existing ice sheet models do?}

FIXME screenshot from Seguinot

\begin{itemize}
\item almost no one is addressing the SIGP directly
    \begin{itemize}
    \item except \cite{WirbelJarosch2020}, but nonscalably and with ``fake ice'' extension
    \item note scalable solution of fixed-geometry Glen-Stokes by Isaac and others \cite{IsaacStadlerGhattas2015}
    \end{itemize}
\item \emph{warning}: this free boundary problem is a barrier to exact numerical mass conservation, regardless of dynamical and/or numerical choices \cite{Bueler2021conservation}
\item what are people doing?  \emph{explicit time-stepping with $s \ge b$ enforced by truncation}
\item \alert{show movie clip}
\end{itemize}
\end{frame}

>>>>

\title{Evolution of \\ ice sheet geometry \\ using Stokes dynamics}

@@

\titlegraphic{\includegraphics[width=0.7\textwidth]{figs/extruded.png} \\ \vspace{-3mm} \includegraphics[width=0.15\textwidth]{figs/uafbw.png}}

%\institute{University of Alaska Fairbanks}

\date{\phantom{foo} \bigskip \bigskip \bigskip \\ SIAM GS21 \\ with assistance from Lawrence Mitchell}

@@

\vspace{-1mm}
\begin{itemize}
\item a non-shallow glacier interacting with the climate
    \begin{itemize}
    \item only the simplest such problem (nonsliding, isothermal)
    \item re~\emph{steady}: solve this and you can handle implicit steps too
    \end{itemize}
\item data given on fixed $\Omega \subset \RR^2$:
    \begin{itemize}
    \item climatic mass balance $a(x,y)$ \hfill $\gets$ \emph{steady climate}
    \item bed elevation $b(x,y)$
    \end{itemize}
\item determine: surface elevation $s(x,y)$ on $\Omega$ and domain $\Lambda_s \subset \RR^3$
\end{itemize}
\end{frame}

@@

\begin{frame}{existing ice sheet models}

\begin{itemize}
\item almost no one is solving the SIGP directly, or implicit time-stepping
    \begin{itemize}
    \item except Wirbel \& Jarosch \cite{WirbelJarosch2020} \dots nonscalable, ``fake ice''
    \item optimal fixed-geometry Stokes solver (Isaac and others \cite{IsaacStadlerGhattas2015})
    \end{itemize}
%\item \emph{warning}: barrier to exact numerical mass conservation \cite{Bueler2021conservation}
\item what are people doing?
    \begin{itemize}
    \item \alert{explicit time-stepping with $s \ge b$ enforced by truncation} (below)
    \end{itemize}
\end{itemize}

\medskip
\begin{columns}
    \column{0.8\textwidth}
        \hfill \includegraphics[width=0.8\textwidth]{figs/seguinot.png}
    \column{0.2\textwidth}
        \scriptsize \emph{show clip from Julien Seguinot using PISM}
\end{columns}
\end{frame}
